| Base de datos de abejas ibéricas \n| Iberian Bees database\n

### 2022-04-23 Manuscript/manuscript.Rmd
Preparing authors

---
title: "| Base de datos de abejas ibéricas \n| Iberian Bees database\n"
author: Ignasi Bartomeus^1^, Jose B. Lanuza^1^, Thomas Wood^2^, Luisa Carvalheiro^3,4^, and a lot of coauthors to be added^5^s
output:
  pdf_document: default
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
csl: ecosistemas.csl
bibliography:
- references.bib
- knitcitations.bib
editor_options:

  chunk_output_type: console
header-includes:
- \DeclareUnicodeCharacter{0301}{*************************************}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}

>>>>

---
title: "| Base de datos de abejas ibéricas \n| Iberian Bees database\n"
author: 
- Ignasi Bartomeus^1^ \orcidlink{0000-0001-7893-4389}
- Jose B. Lanuza^1^ \orcidlink{0000-0002-0287-409X}
- Thomas Wood^2^, 
- Luisa Carvalheiro^3,4^
- Francisco P. Molina^1^

output:
  pdf_document: default
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
csl: ecosistemas.csl
bibliography:
- references.bib
- knitcitations.bib
editor_options:

  chunk_output_type: console
header-includes:
- \DeclareUnicodeCharacter{0301}{*************************************}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
- \usepackage{orcidlink}
